---
title: "4_Pair_camera_data_extraction"
author: "Chris B"
date: "14/04/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
library(stringr)

dir.create("Individual_identification")



# File path to the images
img_loc <- "F:/LosAmigosBackup-18042022/Camera_data/Photos/0_Uploaded To Wildlife Insights"

# File path to the identification folder
img_dest <- "F:/LosAmigos_Cat_Identification/"

```

## Extracting pair camera photos 

If we are going to exploit the paired camera data, we need to extract it and store it in an accessible way. I propose extracting all of the unique events where a jaguar was detected within 10 minutes of one another at paired sites.  

### Import the 10 minute independent data

```{r cars}

# Select the most recent

ind_dat <- read.csv("data/processed-data/LosAmigos_10min_Independent.csv", header=T)
dat <- read.csv("data/processed-data/LosAmigos_all_image_data.csv", header=T)

# Join with the station data to get the "pairs" locations
all.locs <- read.csv("data/raw-data/Camera_locations_master.csv", header=T, sep=",")
str(all.locs)
str(ind_dat)

pair_dat <- left_join(ind_dat, all.locs[, c("Location.Name", "Type")], by=c("deployment_location_id"="Location.Name"))

table(pair_dat$Type)

pair_dat <- pair_dat[pair_dat$Type=="Pairs" & is.na(pair_dat$Type)==F,]

```

## Jaguars

Start with just the jaguars. Match stations with the same location ID and start date?

```{r pressure, echo=FALSE}

dir.create(paste0(img_dest, "/Jaguar/"))
dir.create(paste0(img_dest, "/Jaguar/Pairs"))
dir.create(paste0(img_dest, "/Jaguar/Singles"))

#dep_code <- paste(substr(pair_dat$deployment_id,1,6),substr(pair_dat$deployment_id,13,18), #sep="_")

# Jaguar
tmp_ind <- ind_dat[ind_dat$common_name=="Jaguar",]
tmp_ind$timestamp <- strptime(tmp_ind$timestamp, "%Y-%m-%d %H:%M:%S", tz="UTC")

tmp_raw <- dat[dat$common_name=="Jaguar",]
tmp_raw$timestamp <- strptime(tmp_raw$timestamp, "%Y-%m-%d %H:%M:%S", tz="UTC")
i <- 76
for(i in 1:nrow(tmp_ind))
{
  # Subset all the raw data which occur in at the same station within 30 mins
    tmp_raw$diffs <- difftime(tmp_raw$timestamp, tmp_ind$timestamp[i], units="mins")
    
    tmp_event <- tmp_raw[tmp_raw$deployment_location_id == tmp_ind$deployment_location_id[i] & tmp_raw$diffs > (-30) & tmp_raw$diffs < (30) ,]
  # order the event so the first trigger is first
    tmp_event <- tmp_event[order(tmp_event$timestamp),]
    
  # If a file already exists, skip the loop  
    tmp_name <- paste0(substr(tmp_event$deployment_id[1],1,6), "_", substr(tmp_event$timestamp[1],1,10),"_" ,substr(tmp_event$timestamp[1],12,19)) 
    
    # Replace not allowed characters
    tmp_name <- str_replace_all(tmp_name, ":", "-")
    
    tmp_existing <- c(list.files(paste0(img_dest, "Jaguar/Pairs")), list.files(paste0(img_dest, "Jaguar/Singles")))
    
    # If the file name doesnt exist in the list
    if(!tmp_name %in% tmp_existing)
    {
      # Subset the file locations
      tmp_files <- paste0(img_loc, "/" ,tmp_event$deployment_id,"/",tmp_event$filename)
    
      # Some files are nested within other folders (e.g. )
      if(length(tmp_files[file.exists(tmp_files)==FALSE])>0)
      {
          tmp_sub <- list.files(substr(tmp_files[file.exists(tmp_files)==FALSE], 1,97))
          tmp_files[file.exists(tmp_files)==FALSE] <- paste0(img_loc, "/" ,tmp_event$deployment_id[file.exists(tmp_files)==FALSE],"/",tmp_sub,"/",tmp_event$filename[file.exists(tmp_files)==FALSE])
          
      }
          
      # If detected at two stations in one event - pairs
      if(length(unique(tmp_event$deployment_id))==2)
      {
          dir.create(paste0(img_dest, "/Jaguar/Pairs/", tmp_name))
          file.copy(tmp_files,paste0(img_dest, "/Jaguar/Pairs/", tmp_name) )
      }
  
      # If detected at one station in an event - singles
      if(length(unique(tmp_event$deployment_id))==1)
      {
          dir.create(paste0(img_dest, "/Jaguar/Singles/", tmp_name))
          file.copy(tmp_files,paste0(img_dest, "/Jaguar/Singles/", tmp_name) )
          
      }
    }
    
    
  print(paste(i, "of", nrow(tmp_ind)))
}

# Missing events- the images ARE on wildlife insights - check with Flor
# F:\LosAmigosBackup-18042022\Camera_data\Photos\0_Uploaded To Wildlife Insights\LAC042_C058_050921\IMG_0622.JPG




```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
