---
title: "Los Amigos Camera Trapping Exploration"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r wd, include=FALSE}
# DO NOT RUN THIS IF YOU ARE RUNNING LINE BY LINE - ONLY FOR FINAL REPORT (KNIT)
# Set the WD to the project folder (markdowns working directory when you knit the HTML is where the .rmd is located)
require("knitr")
opts_knit$set(root.dir = '../')

```

```{r non-adjustable options, echo=F, include=F}
#Load Packages
list.of.packages <- c("leaflet", "dplyr", "colortools", "kriging", "corrplot", "lubridate", "kableExtra", "rredlist","sf", "usedist", "ggplot2", "ggpubr", "googledrive", "purrr", "plotly")

# Check you have them and load them
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

lapply(list.of.packages, require, character.only = TRUE)
```

```{r googledrive setup and file import, include=FALSE}
#drive_auth()
# run this line, and enter "Yes". It will open up a browser window, and you'll have to allow access to your Google Drive account

x <- drive_find(n_max = 30)
1
# Create the file
dir.create("data")
dir.create("data/raw-data")


# Wildlife Insights data
# you must have stored you wildlife insights data download packet on google drive - link to it with the URL
folder_url <- "https://drive.google.com/drive/folders/1iFtdGqWDDZw_9JhlgFplhE6Hq9TO0zad"
folder <- drive_get(as_id(folder_url))
csv_files <- drive_ls(folder, type = "csv", recursive=F)

# Clear the folder (overwriting old files)
do.call(file.remove, list(list.files("data/raw-data", full.names = TRUE)))

# Downloads all the files into a subfolder
for (i in 1:nrow(csv_files)) {
    drive_download(as_id(csv_files$id[i]), 
                   path = paste("data/raw-data", csv_files$name[i], sep = "/"), 
                   overwrite=T)
}

# Data entry - target the data entry sheet
folder_url <- "https://drive.google.com/drive/u/0/folders/1nxFVm2Aib1m7TSNEkJjozP-x_GJtM1fo"
folder <- drive_get(as_id(folder_url))
dataentry_files <- drive_ls(folder, recursive=F)

tmp <- dataentry_files[dataentry_files$name %in% c("Entrada_data","Camera_locations_master"),]

# Downloads all the files into a subfolder
for (i in 1:nrow(tmp)) {
    drive_download(as_id(tmp$id[i]), type = "csv",
                   path = paste("data/raw-data", dataentry_files$name[i], sep = "/"), 
                   overwrite=T)
}

```

```{r data setup, include=FALSE}
# Load your data 
dat <- read.csv("data/raw-data/images.csv", header=T)
dep <- read.csv("data/raw-data/deployments.csv", header=T)
pro <- read.csv("data/raw-data/projects.csv", header=T, sep=",")

# EXTRA FOR THIS PROJECT
all.deps <- read.csv("data/raw-data/entrada_data.csv", header=T, sep=",")
colnames(all.deps)[colnames(all.deps)=="deployment_id.LOCATION_CAMERA_STARTDATE"] <- "deployment_id"

# Camera locations master
all.locs <- read.csv("data/raw-data/Camera_locations_master.csv", header=T, sep=",")

# Remove blank rows
all.deps <- all.deps[all.deps$deployment_id!="__",]

# Remove the coordinate information and left_join with the locations master
all.deps$Latitude <- NULL; all.deps$Longitude <- NULL
head(all.deps)
head(all.locs)
all.deps <- left_join(all.deps, all.locs[,c("Location.Name", "Latitude", "Longitude")], by=c("Location"="Location.Name"))

head(dep)
# Timezone  
# They are mainly Reconyx, so use UTC
tz <- "PET"

# Use the strata category to colour plots 
category <- "subproject_name"

# Define a colour from the R options to base the colourscheme
colour <- "lightseagreen"

# Format the date objects
dat$timestamp <- strptime(dat$timestamp, "%Y-%m-%d %H:%M:%S", tz="America/Lima")
dep$start_date <- strptime(dep$start_date, "%Y-%m-%d", tz="UTC")
dep$end_date <- strptime(dep$end_date, "%Y-%m-%d", tz="UTC")

#Calculate days active
dep$days <- dep$end_date-dep$start_date

# Add a deployment_location_id column
dat$deployment_location_id <- substr(dat$deployment_id,1,6)
dep$deployment_location_id <- substr(dep$deployment_id,1,6)
all.deps$deployment_location_id <- substr(all.deps$deployment_id,1,6)

all.deps$subproject_nam <- NA 
all.deps$subproject_nam[substr(all.deps$deployment_id,1,3)=="LAC"] <- "Grids"
all.deps$subproject_nam[substr(all.deps$deployment_id,1,3)=="FEA"] <- "Features"
all.deps$subproject_nam[substr(all.deps$deployment_id,1,3)=="VUL"] <- "Carcass_watching"

# Create a list of currently active deployments in odr of time since deployment
active.deps <- all.deps[all.deps$End.date=="" & is.na(all.deps$End.date)==F,]
active.deps$Start.date <- strptime(active.deps$Start.date, "%d/%m/%y", tz="UTC")
active.deps$Days <- round(as.numeric(strptime(Sys.Date(), "%Y-%m-%d") -  active.deps$Start.date), 1) 

# ADD DEPLOYMENT COVERAGE
tmp <- st_as_sf(all.deps[is.na(all.deps$Longitude)==F,],coords=c("Longitude", "Longitude"),crs=4326)


```

The sub-projects included in this script are **`r unique(dep$subproject_name)`**.

# Active deployment summary
The project currently has `r nrow(active.deps)` cameras active in the field. The project currently spans `r paste(round(as.numeric(st_area(st_as_sfc(st_bbox(tmp)))/1e+6),1), "km^2")`

## Deployment locations [Active]

```{r, echo=F}
# Generate colours to display the category levels - R needs them as a factor
active.deps <- active.deps[is.na(active.deps$Latitude)==F,]
# Create a continuous palette function
pal <- colorNumeric(
  palette = "Reds",
  domain = active.deps$Days)

active.deps$Cols <- pal(active.deps$Days)

# Make a legend key
tmp<- data.frame(Cols=c(active.deps$Cols[active.deps$Days==min(active.deps$Days)][1],
                  active.deps$Cols[nrow(active.deps)/2],
                  active.deps$Cols[active.deps$Days==max(active.deps$Days)][1]),
           Labels=c(active.deps$Days[active.deps$Days==min(active.deps$Days)][1],
                  active.deps$Days[nrow(active.deps)/2],
                  active.deps$Days[active.deps$Days==max(active.deps$Days)][1]))


```

```{r map active, echo=F}

# Count the number of camera ststions
n.stat <- length(unique(active.deps$deployment_id))

m <- leaflet() %>%
  addProviderTiles(providers$Esri.WorldTopoMap, group="Base") %>%
  addProviderTiles(providers$Esri.WorldImagery, group="Satellite") %>%  # Add satellite data
  
  addCircleMarkers(lng= active.deps$Longitude, lat= active.deps$Latitude,
                   color=active.deps$Cols ,
                   popup=paste( active.deps$Location, "-" , active.deps$Days, "days active")) %>%
 
  addLegend("topleft", colors = tmp$Cols,  labels = tmp$Labels,
    title = "Days active",
    labFormat = labelFormat(prefix = "$"),
    opacity = 1
  ) %>%
  # Layers control
  addLayersControl(
    baseGroups = c("Satellite", "Base"),
    options = layersControlOptions(collapsed = FALSE)
  )
m

```

### Active locations by subproject

```{r active summaries, echo=F}
tmp <- as.data.frame(table(active.deps$subproject_nam))

p1 <- plot_ly(
  x=tmp$Var1,
  y=tmp$Freq,
  name = "Active deployments",
  type = "bar"
) %>%
  layout(plot_bgcolor = "#f5f5f5", 
         xaxis = list(title = 'Sub-project'), 
         yaxis = list(title = 'Active deployments'),
         title="Active deployments")

tmp <- as.data.frame(table(dep$subproject_name))

p1

```

### List of active deployment locations

In order to help decide the next cameras to check - we also list the currently active cameras below (with the longest running first):

```{r, echo=F}
tmp <- active.deps[, c("deployment_id", "Location", "Days")]
tmp <- tmp[order(tmp$Days, decreasing=T),]

tmp <- left_join(tmp, all.locs, by=c("Location"= "Location.Name"))

tmp[,c("deployment_id", "Location",  "Days", "Project" ,"Group")] %>%
  kbl() %>%
  kable_styling(full_width = T) %>%
  column_spec(1, bold = T, border_right = T )%>%
  scroll_box( height = "200px")

```

# All deployments
To date we have deployed cameras in `r length(unique(all.deps$deployment_location_id))` locations. 

```{r, echo=F, include=F}
# Generate colours to display the category levels - R needs them as a factor
table(all.deps$Subprojet)
all.deps[,category] <- factor(all.deps[,"Subprojet"])
col.cat <- wheel(colour, num = length(levels(all.deps[,category])))
all.deps$Cols <- col.cat[all.deps[,category]]
```

```{r map, echo=F}

# Count the number of camera ststions
n.stat <- length(unique(all.deps$deployment_id))

m <- leaflet() %>%
  addProviderTiles(providers$Esri.WorldTopoMap, group="Base") %>%
  addProviderTiles(providers$Esri.WorldImagery, group="Satellite") %>%  # Add satellite data
  
  addCircleMarkers(lng= all.deps$Longitude, lat= all.deps$Latitude,
                   color= all.deps$Cols,
                   popup=paste( all.deps$Location,  all.deps[,category])) %>%
 addLegend("topleft", colors = col.cat,  labels = levels( all.deps[,category]),
    title = category,
    labFormat = labelFormat(prefix = "$"),
    opacity = 1
  ) %>%
  # Layers control
  addLayersControl(
    baseGroups = c("Satellite", "Base"),
    options = layersControlOptions(collapsed = FALSE)
  )
m

```

# Wildlife Insights Summary

To date, `r Sys.Date()`, we have `r nrow(dat)` images. They were identified by the following mechanism:

```{r, echo=F}
par(mfrow=c(1,1))
tmp <- as.data.frame(table(dat$identified_by=="Computer vision"))

tmp$Type <- "Labelled"
tmp$Type[tmp$Var1==TRUE] <- "To label"

f1 <- plot_ly(tmp,y=~tmp$Freq, x=tmp$Type,  type="bar", name=tmp$Type) %>% 
        layout(yaxis = list(title = 'Images'), barmode = 'group')

f1
```

The breakdown by labeler is as follows:

```{r, echo=F}
tmp2 <- as.data.frame(table(dat$identified_by[!dat$identified_by%in% c("Computer vision", "")]))

colnames(tmp2)[1] <- "Person"

f2 <- plot_ly(tmp2,y=~tmp2$Freq, x=tmp2$Person,  type="bar", name=tmp2$Person) %>% 
        layout(yaxis = list(title = 'Images labelled'), barmode = 'group')


f2

```

## Species labels

```{r, echo=F}
# Reduce to verfied data
vdat <- dat[!dat$identified_by %in% c("Computer vision", ""),]
# Remove blanks
vdat$sp <- paste(vdat$genus, vdat$species)
vdat <- vdat[vdat$is_blank==0,]
vdat <- vdat[vdat$species!="No CV Result",]
vdat <- vdat[vdat$common_name!="Blank",]

# Do all species with a latin name have a common name - YES use common name
#as.data.frame(table(paste(vdat$sp, vdat$common_name)))

# if the species name is blank it must be to family, order or class level
```

To date we have `r `nrow(vdat)` image labels verified by human observers (after removing `r nrow(dat[dat$is_blank==1 | dat$species=="No CV Result" | dat$common_name =="Blank",])` blanks). The species categories are as follows:

```{r, include=F}

# OLD VERSION
n.loc <- length(unique(dep$deployment_location_id))

layout(matrix(c(1,1,2), 1, 3, byrow = TRUE))
det.sum.total <- as.data.frame(count(vdat[vdat$is_blank==0,], common_name))
det.sum.total <- det.sum.total[order(det.sum.total$n),]

par(mar=c(5,16,1,1))
barplot(det.sum.total$n, names.arg = paste0(det.sum.total$common_name, 
                                           " (n =", det.sum.total$n,")")   , las=1, cex.names=1, xlab="Total detections", horiz=T)
i <-1


for(i in 1:nrow(det.sum.total))
{
  tmp <- subset(vdat, common_name==det.sum.total$common_name[i])
  det.sum.total$Locations[i] <- length(unique(tmp$deployment_location_id))
}
par(mar=c(5,1,1,1))

barplot(det.sum.total$Locations/n.loc, las=1, cex.names=0.7, xlab="Proportion of sites detected", horiz=T, xlim=c(0,1))
abline(v=1, lty=2)

```

To date we have `r length(unique(vdat$common_name))` unique classifications. Of these, `r length(unique(vdat[vdat$species!="",]$sp))` are to full species level, `r length(unique(vdat[vdat$species=="",]$genus))` to genus level, the rest are higher (family/order). 

Note you can use the slider bar at the bottom to control the the x-axis extent. 

```{r, echo=F}
# MAke it in plotly?
#Order

det.sum.total$order <-1:nrow(det.sum.total)

yform <- list(categoryorder = "array",
              categoryarray = det.sum.total$common_name,
              tickfont = list(size = 7))

xform <- list(rangeslider = list(type = "n"))

fig <- plot_ly(x = det.sum.total$n, y = det.sum.total$common_name, type = 'bar', orientation = 'h',
               height=2000)%>% 
 layout(yaxis = yform, xaxis=xform)

fig

```

# Diel time
For any species detected more than 10 times, we will plot when they were detected:

```{r, echo=F, warning=F, message=F}
vdat$hours <- hour(vdat$timestamp) + minute(vdat$timestamp)/60 + second(vdat$timestamp)/(60*60)


yform <- list(categoryorder = "array",
              categoryarray = det.sum.total$common_name,
              tickfont = list(size = 7))

fig <- plot_ly(x = vdat$hours, y = vdat$common_name,type="scatter",
               height=2000, text=vdat$deployment_id, hoverinfo='text',
               mode   = 'markers',
               marker = list(size = 5,
                             color = 'rgba(50, 100, 255, .2)',
                             line = list(color = 'rgba(0, 0, 0, 0)',
                                         width = 0))) %>% 
              layout(yaxis = yform)

fig

```

# Detection check

We also need to check if all of the deployments in Wildlife Insights have associated image data.

Of the deployments currently in Wildlife Insights, `r paste0((length(dep$deployment_id[dep$deployment_id %in% dat$deployment_id])/nrow(dep))*100, "%")` of deployments have associated image data.

*Note - our current workflow should mean that deployments ALWAYS have image data. If the percentage is <100% then there is a problem*

We can also check to see if any deployments need truncating - for example if the camera ceased to be active:

```{r}
# Plot the start and end date for each deployment
fig <- plot_ly(x = dep$start_date[1:5], y = dep$deployment_id[1:5],type="scatter",
               height=2000)
fig
remove(f1)

```



# Meta data

Summary information for the project:

```{r, echo=F}
t(pro) %>%
  kbl() %>%
  kable_styling(full_width = T) %>%
  column_spec(1, bold = T, border_right = T)


```


